---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

All based on https://juliasilge.com/blog/word-associations/.


First, the libraries:
```{r}
library(tidyverse)
library(here)
library(igraph)
library(ggraph)
library(tidygraph)
library(knitr)
library(magrittr)
```

Then import the data:
```{r}
swow_raw <- read_csv(here("SWOW-EN.R100.csv"))
```

Now create forward associations
```{r}
swow_forward <- swow_raw %>% 
    select(from = cue, to = R1, gender, age, nativeLanguage) %>%
    bind_rows(
        swow_raw %>% 
            select(from = R1, to = R2, gender, age, nativeLanguage)
    ) %>%
    bind_rows(
        swow_raw %>% 
            select(from = R2, to = R3, gender, age, nativeLanguage)
    ) %>%
    filter(!is.na(to))
```

And limit this to "pleasure" as the first word
```{r}
swow_pleasure <- swow_forward %>%
    filter(from == "pleasure")
```

Lets get a picture as some sort of sanity check

```{r}
swow_pleasure %>%
  count(to, sort = TRUE) %>%
  top_n(15, n) %>% 
  ggplot(aes(x = fct_reorder(to, n), y = n)) + 
  geom_col() + 
  coord_flip()
```
Ok, that looks legit.

What we want is the ego network of "pleasure" from the whole froward association network.

Then we'll add some node characteristics
* Centrality
* Community

```{r}
pleasure_ego_undirected <- swow_forward %>%
  select(from, to) %>%
  graph_from_data_frame() %>%
  make_ego_graph(nodes = "pleasure", order = 1, mode = "all") %>%
  extract2(1) %>%
  as_tbl_graph(directed = FALSE) %>%
  mutate(community = as.factor(group_walktrap())) %>%
  mutate(centrality = centrality_degree())
```

Lets make a list of the nodes so we can see which ones we want to remove.

```{r}
list_nodes <- pleasure_ego_undirected %>%
  activate(nodes) %>%
  as.tibble() %>%
  kable()
```

Lets list the ones we want to remove so we can filter them out

```{r}
manual_removal <- c("vagina", "penis", "sex", "gay", "intimate", "gender", "bitch", "drug", "fuck", "sexual", "orgasm", "erection", "pleasure", "lesbian", "bondage", "kinky", "erotic", "nudity", "hormones", "taboo", "oral", "porn", "semen", "masturbation", "penetration", "horny", "clitoris", "vibrator", "vibration", "breastfeeding", "masturbate", "anal", "blowjob", "ejaculation", "sadomasochism", "cum", "sec", "spanking", "wan", "hand job", "fellatio", "thighs", "genitalia", "tossing", "sex-drive", "flagellation", "erotica", "titlometre", "laisure", "onan", "co,pletion")
```


Lets make a network that has 
* Only the strongest edges (too many connections clutters up the picture and takes ages to plot)
* No nodes we want to filter out
* Only the most connected nodes

Then we'll have to recalculate centrality and community.

```{r}
pleasure_ego_trim <- pleasure_ego_undirected %>%
  activate(edges) %>%
  group_by(from, to) %>%
  mutate(weight = sum(n())) %>%
  ungroup() %>%
  distinct() %>%
  filter(weight > 10) %>%
  activate(nodes) %>%
  filter(!name %in% manual_removal) %>%
  top_n(100, centrality) %>%
  mutate(community = as.factor(group_walktrap())) %>%
  mutate(centrality = centrality_degree()) %>%
  mutate(name = as.character(name))
```

There might be too many communities (some of which might have very few nodes in them). Lets check it out.

```{r}
pleasure_ego_trim %>%
  activate(nodes) %>%
  as.tibble() %>%
  count(community) %>%
  ggplot(aes(x = fct_reorder(community, n), y = n)) + 
  geom_col() + 
  coord_flip()
```

Ok, so there are four serious communities. Lets clump the others into a single one. And while we're at it, giove the nodes an ID factor:

```{r}
pleasure_ego_trim <- pleasure_ego_trim %>%
  activate(nodes) %>%
  mutate(community = fct_collapse(community, "5" = c("5", "6", "7", "8", "9", "10", "11"))) %>%
  mutate(id = row_number()) %>%
  as_tbl_graph()
```

Lets have a look:
```{r}
ggraph(pleasure_ego_trim, layout = 'graphopt', charge = 1) + 
  geom_edge_link(alpha = .1, colour = "white") + 
  geom_node_text(aes(label = name, colour = community), nudge_y = 200) + 
  geom_node_point(aes(colour = community, size = centrality)) +
  guides(colour = FALSE, alpha = FALSE, size = FALSE) + 
  theme_graph(background = "black")
```

Let's test this out with two words selected in by the app:
```{r}

selected <- c("holiday", "happiness")

ggraph(pleasure_ego_trim, layout = 'graphopt', charge = .05) + 
  geom_edge_link(alpha = .1, colour = "white") + 
  geom_node_text(aes(label = if_else(name %in% selected, as.character(name), ""), colour = community), nudge_y = 100) + 
  geom_node_point(aes(alpha = if_else(name %in% selected, 1, 0), colour = community, size = centrality)) +
  guides(colour = FALSE, alpha = FALSE, size = FALSE) + 
  theme_graph(background = "black")
```

So, let's export an RDS file of pleasure_ego_trim that can be used in the app.

```{r}
saveRDS(pleasure_ego_trim, here("pleasure_mod_app", "pleasure_ego_trim.rds"))
```

Then a couple of other bits so that the excellent designers can make this better...

First, a list of the nodes that will be in the final graph with degree and community saved as a csv.

```{r}
pleasure_words <- pleasure_ego_trim %>%
  activate(nodes) %>%
  as.tibble() %>%
  write.csv(here("pleasure_words.csv"), row.names = FALSE)
  
```

And the edgelist.

```{r}
pleasure_connections <- pleasure_ego_trim %>%
  activate(edges) %>%
  as.tibble() %>%
  write.csv(here("pleasure_connections.csv"), row.names = FALSE)
```


